Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-18 final_metrics_analysis.Rmd
expl priors race

```{python exploratory priors by race}
priors_by_race = sns.countplot(x="race", hue="priors_count", data=df_viz, palette=workshop_palette)

plt.title('Priors Count by Race')
plt.show()
```

>>>>

```{python exploratory priors by race}
#priors_by_race = sns.countplot(x="race", hue="priors_count", data=df_viz, palette=workshop_palette)

#plt.title('Priors Count by Race')
#plt.show()
```
